Gaze-dependent evidence accumulation predicts multi-alternative risky choice behaviour

### 2021-02-04 manuscript/main.tex
capital letters for GLA
fixed a typo and a reference

The switchboard analysis included different eye-movement related nodes, such as attribute and alternative wise gaze biases or gaze-dependent leakage and inhibition, so that the mechanisms that describe the data best can be identified and their relative contribution to model fit can be measured. All switchboard models resembled the general form of the gaze-dependent accumulation model presented in \textcite{glickman2019FormationPreferenceRisky} and the GLA adaptation to three items (see above and Figure \ref{fig:switchboard} a for a schematic). Here, evidence $X_i$ in favour of each item is accumulated over individual fixations. Accumulation can be subject to gaze-discount effects (so that non-fixated items accumulate less evidence), leak and inhibition over time. Choice probabilities are computed using a soft-max function (Equation \ref{eq:softmax}) over the final accumulator values. The general accumulation framework (in vector form, parallel for each item) is then given by

@@

% Supplementary Figure: GLA estimates and correlations
\begin{figure}[ht!]
\begin{centering}
\includegraphics[scale=1]{../figures/S_gla-estimates.pdf}
\caption{\textbf{GLA maximum likelihood estimates and relationships between parameters.} $\alpha$ is the utility parameter. $\beta$ is the inverse temperature parameter of the choice rule (0 = random choice). $\gamma$ is the probability weighting parameter (1 = linear weighting). $\lambda$ is the leak parameter (0 = perfect memory, 1 = full leak of all previous information). $\theta$ is the gaze-discount parameter (1 = no gaze-discount, 0 = maximum gaze-discount).}
\label{fig:gla-estimates}
\end{centering}
\end{figure}
\clearpage

>>>>

The switchboard analysis included different eye-movement related nodes, such as attribute and alternative wise gaze biases or gaze-dependent leakage and inhibition, so that the mechanisms that describe the data best can be identified and their relative contribution to model fit can be measured. All switchboard models resembled the general form of the gaze-dependent accumulation model presented in \textcite{glickman2019FormationPreferenceRisky} and the GLA adaptation to three items (see above and Figure \ref{fig:switchboard}a for a schematic). Here, evidence $X_i$ in favour of each item is accumulated over individual fixations. Accumulation can be subject to gaze-discount effects (so that non-fixated items accumulate less evidence), leak and inhibition over time. Choice probabilities are computed using a soft-max function (Equation \ref{eq:softmax}) over the final accumulator values. The general accumulation framework (in vector form, parallel for each item) is then given by

@@

% Supplementary Figure: GLA estimates and correlations
\begin{figure}[ht!]
\begin{centering}
\includegraphics[scale=1]{../figures/S_GLA-estimates.pdf}
\caption{\textbf{GLA maximum likelihood estimates and relationships between parameters.} $\alpha$ is the utility parameter. $\beta$ is the inverse temperature parameter of the choice rule (0 = random choice). $\gamma$ is the probability weighting parameter (1 = linear weighting). $\lambda$ is the leak parameter (0 = perfect memory, 1 = full leak of all previous information). $\theta$ is the gaze-discount parameter (1 = no gaze-discount, 0 = maximum gaze-discount).}
\label{fig:gla-estimates}
\end{centering}
\end{figure}
\clearpage
